\thetitle

### 2008-06-26 letter.tex
Letter now explains why mixed cond. model was omitted.

The simulation results supporting our claim that the general matrix model sufficiently realistic as a generative workload model remains the unchanged, with one exception:
the \model{mixed conditional} model (previously called \model{mixed regular}).
There was an error in the code generating traffic for this model, which caused the simulation results to be incorrect;
we have corrected this error.

>>>>

The simulation results supporting our claim that the general matrix model sufficiently realistic as a generative workload model remains the unchanged, with one exception:
the \model{mixed conditional} model (previously called \model{mixed regular}).
There was an error in the code generating traffic for this model, which caused the simulation results to be incorrect.
Upon correcting this error, we found that the mixed model performed identically to the source and destination based models.
These results were therefore deemed uninteresting and omitted.
